### 2024-11-28 CV2/papers.tex
update website

\textbf{Decentralized Optimization with Coupled Constraints} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov). \textit{arXiv preprint arXiv:2407.02020}, 2024.

@@

\textbf{Decentralized Finite-Sum Optimization over Time-Varying Networks} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2402.02490}, 2024.

>>>>

\textbf{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms} (Dmitry Kovalev, Ekaterina Borodich). \textit{arXiv preprint arXiv:2411.14601}, 2024.
\textbf{Decentralized Optimization with Coupled Constraints} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev). \textit{arXiv preprint arXiv:2407.02020}, 2024.

@@

\textbf{Decentralized finite-sum optimization over time-varying networks} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov, Dmitry Kovalev). \textit{arXiv preprint arXiv:2402.02490}, 2024.
